### 2020-08-06 paper.tex
Code Subjects

The subjects for our study were required to have experience in developing applications with RxJS. We did not distinguish between frontend or backend engineers, so in the end, we were able to find four subjects willing to participate in our experiment. We were interested to see how the subjects apply debugging techniques they would use in an everyday situation at their jobs. Hence we decided to conduct the experiment in a somewhat uncontrolled environment where the subjects used their own devices with their development environments of personal preference. Our objective for the experiment was communicated as broad as possible to prevent bias: ``We are interested in how \emph{you} debug a problem'' did not mention the hypothesis by intention.

@@

\subsection{Results}

After the subjects got a feel for what the application on front of them should do, all of them used the provided test suite to check what features do not work as expected and tried to recreate the failing behavior in the UI manually. Two of them used the traditional debugging tools provided by their browser or IDE to step through parts of the code trying to understand what triggered the failing tests.

For both problems given, we could observe all subjects to make use of manually added trace log statements either within an existing arrow function or using the \mintinline{TypeScript}{tap} operator. Neither did any of them use additional external tools where they put parts of the code for further inspection nor did they install additional debugging libraries like rxjs-spy.
After the 25 minutes of the second block exceeded, one subject noted that they would have usually started now to decompose the problem into smaller pieces and observe their behavior more isolated.

The survey responses showed that 75\% of the subject population had two or more years of experience with RxJS. Where all of them use RxJS to develop frontend applications, one subject declared having RxJS used for backend development as well. When asked what tools they usually use for debugging, only one subject told not to use the traditional debugger of their browser or IDE. Two of them leverage additional tracing functionality of rxjs-spy, and all of them use manual log statements.

>>>>

The subjects for our study were required to have experience in developing applications with RxJS. We did not distinguish between frontend or backend engineers, so in the end, we were able to recruit four subjects willing to participate in our experiment. We were interested to see how the subjects apply debugging techniques they would use in an everyday situation at their jobs. Hence we decided to conduct the experiment in a somewhat uncontrolled environment where the subjects used their own devices with their development environments of personal preference. Our objective for the experiment was communicated as broad as possible to prevent bias: ``We are interested in how \emph{you} debug a problem'' did not mention the hypothesis by intention.

@@

\subsection{Study Execution and Results}

After the subjects S1 to S4 got a feel for what the application on front of them should do, all of them used the provided test suite to check what features do not work as expected and tried to recreate the failing behavior in the UI manually. Two of them used the traditional debugging tools provided by their browser or IDE to step through parts of the code trying to understand what triggered the failing tests.

For both problems given, we could observe all subjects to make use of manually added trace log statements either within an existing arrow function or using the \mintinline{TypeScript}{tap} operator. Neither did any of them use additional external tools where they put parts of the code for further inspection nor did they install additional debugging libraries like rxjs-spy.
After the 25 minutes of the second block exceeded, S2 noted that they would have usually started now to decompose the problem into smaller pieces and observe their behavior more isolated.

The survey responses showed that 75\% (S2 to S4) of the subject population had two or more years of experience with RxJS. Where all of them use RxJS to develop frontend applications, S4 declared having RxJS used for backend development as well. When asked what tools they usually use for debugging, only S1 stated not to use the traditional debugger of their browser or IDE. S1 and S3 leverage additional tracing functionality of rxjs-spy, and all of them use manual log statements.
